---
title: "R Notebook"
output: html_notebook
---

```{r knn-pkgs, message=FALSE}
# Helper packages
library(dplyr)      # for data wrangling
library(ggplot2)    # for awesome graphics
library(rsample)    # for creating validation splits
library(recipes)    # for feature engineering

library(ISLR)       # Dataset

# Modeling packages
library(caret)       # for fitting KNN models
```

Using the ISLR::Default dataset where the default variable is the response variable:

*Q1* Apply a KNN model with all features. Use a grid search to assess values of k ranging from 2-200 that seeks to optimize the “ROC” metric.

```{r}
islr <- ISLR::Default
islr

# Create a hyperparameter grid search
hyper_grid <- expand.grid(
  k = floor(seq(2,200))
)

# Fit knn model and perform grid search
knn_grid <- train(
  data = islr, 
  method = "knn", 
  tuneGrid = hyper_grid,
  metric = "ROC"
)

ggplot(knn_grid)

```


```{r}
# Split
set.seed(123)
split <- initial_split(islr, prop = .7, strata = "default")
train <- training(split)

# Create blueprint
blueprint <- recipe(default ~ ., data = train) %>%
  step_nzv(all_nominal()) %>%
  step_integer(matches("default|student")) %>%
  step_dummy(all_nominal(), -all_outcomes(), one_hot = TRUE) %>%
  step_center(all_numeric(), -all_outcomes()) %>%
  step_scale(all_numeric(), -all_outcomes())

# Create a resampling method
cv <- trainControl(
  method = "repeatedcv", 
  number = 10, 
  repeats = 5,
  classProbs = TRUE,                 
  summaryFunction = twoClassSummary
)

# Create a hyperparameter grid search
hyper_grid <- expand.grid(
  k = floor(seq(1, nrow(train)/3, length.out = 20))
)

# Fit knn model and perform grid search
knn_grid <- train(
  blueprint, 
  data = train, 
  method = "knn", 
  trControl = cv, 
  tuneGrid = hyper_grid,
  metric = "ROC"
)

```

*Q2* Plot the grid search performance.

```{r}
ggplot(knn_grid)

ggplot(hyper_grid)
```

*Q3* What value for K optimizes model performance? What does this tell you about your data?
```{r}

```

*Q4* Plot the ROC curve for the optimal model.
```{r}

```

*Q5* Which 10 features are considered most influential? Are these the same features that have been influential in previous models?
```{r}

```

*Q6* Now perform questions 1-5 for the built in iris data where species is the response variable.
```{r}

```

